---
title: "Carryover_Imputation"
author: "Cort W. Rudolph"
date: "10/25/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Install & Load Required Packages
```{r}
# install.packages("tidyverse")
# install.packages("lavaan")
# install.packages("multilevel")
# install.packages("lme4")
# install.packages("mice")
#install.packages("mitml")

library(tidyverse)
library(lavaan)
library(multilevel)
library(lme4)
library(mice)
library(mitml)

```


## Simulate Population Model

```{r}
pop_model <- '

# Define X
i_x =~ 1*x1 + 1*x2 + 1*x3 + 1*x4
s_x =~ 0*x1 + 1*x2 + 2*x3 + 3*x4

i_x ~~ 1 * i_x    # Variance of intercept
s_x ~~ 0.25 * s_x # Variance of slope
s_x ~~ 0.15 * i_x # Covariance of intercept and slope for X

x1 ~~ 0.5 * x1
x2 ~~ 0.5 * x2
x3 ~~ 0.5 * x3
x4 ~~ 0.5 * x4

i_x ~ 1 * 1
s_x ~ 0.5 * 1




# Define Y
i_y =~ 1*y1 + 1*y2 + 1*y3 + 1*y4
s_y =~ 0*y1 + 1*y2 + 2*y3 + 3*y4

i_y ~~ 1 * i_y    # Variance of intercept
s_y ~~ 0.25 * s_y # Variance of slope
s_y ~~ 0.15 * i_y # Covariance of intercept and slope for X

y1 ~~ 0.5 * y1
y2 ~~ 0.5 * y2
y3 ~~ 0.5 * y3
y4 ~~ 0.5 * y4

i_y ~ 1 * 1
s_y ~ 0.5 * 1


# Covariance between of X & Y intercepts/slopes
i_x ~~ .25 * i_y
s_x ~~ .15 * s_y

i_x ~~ .25 * s_y
s_x ~~ .25 * i_y

'
```

# Create Poplation Data (N = 500,000)
```{r}
set.seed(1)
populationData<-lavaan::simulateData(pop_model, sample.nobs=500000) 
```

# Confirm Parameter Estimates in Population
```{r}
model <- '
i_x =~ 1*x1 + 1*x2 + 1*x3 + 1*x4
s_x =~ 0*x1 + 1*x2 + 2*x3 + 3*x4

i_y =~ 1*y1 + 1*y2 + 1*y3 + 1*y4
s_y =~ 0*y1 + 1*y2 + 2*y3 + 3*y4
'
```

```{r}
pop_fit<-growth(model, populationData)
parameterestimates(pop_fit)[28:34,1:5] 
```

# Create Unique ID Variable
```{r}
populationData$ID <-rep(1:nrow(populationData))
```


# Sample Size Specification
```{r}
N <- 100
```


# Sample N Cases from Population
```{r}
set.seed(1)
sampleData<-populationData %>%
  sample_n(., size=N, replace=FALSE)
```

# Confirm Parameter Estimates in Sample
```{r}
sample_fit<-growth(model, sampleData)
parameterestimates(sample_fit)[28:34,] 
```

# Restructure Sample Data (Wide to Long)
```{r}
# 2. Convert to Long (i.e., Univariate)
dvlist <- list(c(1:4),c(5:8)) #Create a list of DV's 
names(dvlist) <- c("X","Y") #Names for univariate output

#Transform the data into univariate form with multiple level-1 variables
sampleDataLong <- mult.make.univ(x=sampleData,dvlist=dvlist)  
```

# Ampute MAR Data (i.e., remove X% cases at random)

# % Data to remove
```{r}
PCT <- .50
```


```{r}
# Select relevant columns
sampleDataLongMissing <- sampleDataLong %>%
  dplyr::select(ID, TIME, X, Y)

# Amputation
set.seed(1)
temp<-ampute(sampleDataLongMissing[,3:4], prop = PCT, mech = "MAR")

# Bind amputed data together with complete data
temp<-as.data.frame(temp$amp)
temp <- rename(temp, X_missing = "X", Y_missing = "Y")
sampleDataLongMissing<-cbind(sampleDataLongMissing, temp)
```

<!-- # Equivalent Means of COI with Missing 1st TimePoints-- Proof of Concept -->
<!-- ```{r} -->
<!-- # a <- data.frame(col1 = c(1,1,1,1,2,2,2,2,3,3,3,3),  -->
<!-- #                 col2 = 1:12, -->
<!-- #                 col3 = 1:12,  -->
<!-- #                 col4 = c(4,NA,NA,4,NA,5,NA,5,NA,NA, 6, NA)) -->
<!-- # a -->
<!-- #  -->
<!-- # a %>% -->
<!-- #   group_by(col1) %>% -->
<!-- #   tidyr::fill(col4) -->
<!-- #  -->
<!-- # a %>% -->
<!-- #   group_by(col1) %>% -->
<!-- #   mutate(col4_COI = zoo::na.locf(col4, na.rm = FALSE)) -->
<!-- ``` -->


# Carryover Imputation (n.b. properly Accounts for Missing First Timepoint!)
using `zoo::na.locf`
```{r}
sampleDataLongMissing <-
sampleDataLongMissing %>%
  dplyr::group_by(ID) %>%
  dplyr::mutate(X_COI=zoo::na.locf(X_missing, na.rm = FALSE),
                Y_COI=zoo::na.locf(Y_missing, na.rm = FALSE))
```

# Correlations
```{r}
sampleDataLongMissing[,c(1,3:8)] %>% 
  psych::statsBy(., group="ID") %>%
  print(short=FALSE)
```

# LME Model Complete
```{r}
completeModel<-lmer(Y~TIME*X+(1|ID), sampleDataLongMissing)
```

# LME Model Missing
```{r}
missingModel<-lmer(Y_missing~TIME*X_missing+(1|ID), sampleDataLongMissing)
```

# LME Model COI
```{r}
coiModel<-lmer(Y_COI~TIME*X_COI+(1|ID), sampleDataLongMissing)
```

# Table
```{r}
sjPlot::tab_model(completeModel, missingModel, coiModel,
                  show.se=TRUE,
                  show.ci=FALSE,
                  show.p = TRUE,
                  digits = 3,
                  string.se = "SEs")
```





# PAN Imputation via `mitml`

```{r}
# https://cran.r-project.org/web/packages/mitml/vignettes/Introduction.html

sampleDataLongMissingPAN <- sampleDataLongMissing %>%
  ungroup() %>%
  dplyr::select(ID, TIME, Y_missing, X_missing)

str(sampleDataLongMissingPAN)

# Imputation Model
fml <- Y_missing + X_missing ~ 1 + TIME + (1|ID)
imp <- mitml::panImpute(sampleDataLongMissingPAN, formula=fml, n.burn=5000, n.iter=500, m=100)
#imp <- mitml::jomoImpute(IMPUTATION.SS, formula=fml, n.burn=100, n.iter=100, m=5)

implist <- mitmlComplete(imp, "all")
summary(imp)

fit <-  with(implist,lmer(Y_missing ~ TIME*X_missing + (1|ID)))

testEstimates(fit, var.comp=TRUE)
```

